\documentclass{article}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{soul}
\usepackage{chemformula}


\pagestyle{fancy}
\fancyhf{}
\rhead{11.04.2019}
\lhead{Experiment \#7}
\rfoot{Page \thepage}

\begin{document}
\section*{Experiment 7}

\section{Aim}
Test 1, 2, and 3 hour immersion times 

\section{Method}
\subsection{Preparation}
\subsubsection{Ag Precursor Solution}
\begin{itemize}
    \item  $4 \times 1.5$g solution of \ch{AgCF3COO} 35\% wt
\end{itemize}

\subsubsection{Ascorbic Acid}
\begin{enumerate}
    \item 0.032 wt: 10ml
    \item 0.016 wt: 10ml
    \item 0.008 wt: 10ml
\end{enumerate}

\subsubsection{Spandex Fibers}
18 Fibers in total:
\begin{itemize}
    \item $18\times 4$cm
\end{itemize}

\subsection{Procedure}
\begin{itemize}
    \item Immerse 6 fibers in each precursor solution
    \item \textit{Precursor Immersion Time}: 1 hour
    \item Remove and allow to dry. \underline{Dried on tissue}
    \item Separate the fibers into 3 sets of 3 pairs.
    \item Immerse each set with a different concentration of Ascorbic acid
    \item \textit{Ascorbic Acid Immersion Time}: 1, 2, and 3 hours
    \item Remove the fibers from the Ascorbic acid at the set time intervals 
    \item Allow to dry, then measure resistance.
\end{itemize}

\subsection{Documentation of Experiment}
Precursor:
\begin{enumerate}
    \item 0.702g (AgCF3COO) $\rightarrow$ fill to 1300g 
    \item 0.699g (AgCF3COO) $\rightarrow$ fill to 1300g 
    \item 0.742g (AgCF3COO) $\rightarrow$ fill to 1400g 
\end{enumerate}
Ascorbic Acid:
\begin{enumerate}
    \item 0.342g (Ascorbic acid) + 10.69g (water)
    \item 0.167g (Ascorbic acid) + 10g (water)
    \item 0.081g (Ascorbic acid) + 10g (water)
\end{enumerate}


NB: One of the fibers in the 0.016 wt - 2hr immersion was uncovered when I went to take it out - I suspect this was due to the opening of the drawer and hence would not have a large impact on the experiment.


\section{Result}

\begin{table}[h!]
\centering
\begin{tabular}{ |c|c|c|c| } 
 \hline
& \multicolumn{3}{l|}{Immersion (Hrs)} \\ \hline
Ascorbic Acid Conc (wt) & 1 & 2 & 3  \\ 
 \hline
 0.032  & X & X & X \\ 
 & X & X   &  \\ 
 \hline
 0.016 & X & 300$\Omega$ & 30$\Omega$ \\ 
& X & X & X  \\ 
 \hline
  0.008 & 50$\Omega$ & X & X\\ 
& 80$\Omega$ & X & X  \\ 
 \hline
\end{tabular}
 \caption{Resistance of Fibers}
\label{table:1}
\end{table}
\pagebreak
\section{Conclusion}
\begin{itemize}
    \item 2 conducting fibers with 0.008 wt and 1hr immersion - further immersion time did not seem to improve conductivity and the 4 fibers with 2hr and 3hr immersion times were not conducting.
    \item 1 conducting fiber with 0.016 wt and 2hr immersion.

    \item 1 conducting fiber with 0.016 wt and 3 hr immersion.
\end{itemize}


Lower concentration and longer immersion times seem to be more effective.

Fibers may be not completely covered by the reducing agent (e.g. moving the drawer could cause the liquid to move and uncover the fiber) - avoid  by using more ascorbic acid and filling the petri dish.

\end{document}


